---
title: "Exercise RMrkdown and reproductibility course"
author: "The EDB RMarkdown superstar learning team"
date: "01/03/2022"
output: 
  html_document:
    number_sections: true
    toc: true
    theme: united
    highlight: tango
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = ".")
```

# Introduction

This exercise is the best way to practice `RMarkdown` [@salinas2020r] now that you have had an overview of how it works. The principle is that you want to produce a copy of this `pdf` file. We provide most of the `R code`, because the scope is to work on the `RMarkdown` [@xie2018r] integration, not on the `R code`. 

# Starters

You want to create a new `Rmarkdown` file and save it in the `Exercise` folder.

# Load packages

What packages will I need? Well I can fill that in later anyway.

BTW: To add a new code chunck the keyboard shortcut is `Ctrl` + `Alt` + `i`.
Or use the insert button on the top left side of this window.
```{r , echo=FALSE, include=FALSE}
library(ggplot2)
library(kableExtra)
library(readxl)
library(corrplot)
```


# Research compendium

Let's organize our project. We create a folder called `data` and list the files in the current working folder.

```{r, echo=TRUE, include=TRUE}
system("mkdir -p data")
list.files(path = ".")
list.dirs(path = ".", full.names = TRUE, recursive = TRUE)
```

We can now move the `datasets.xls` file (main folder to the `Exercise/data` folder).

# Load the project data

We'll use the mtcars dataset that we"ll load from the `datasets.xls` file.
He we do not provide the code because it is part of the exercise. 
```{r, echo=FALSE, include=FALSE}
my_mtcars <- as.data.frame(read_excel("data/datasets.xlsx",sheet = "mtcars"))
```


# Analyze the data

## Get a look at the data
```{r ,echo=TRUE, include=TRUE}
#summary(my_mtcars)
my_mtcars2 <- within(my_mtcars, {
   vs <- factor(vs, labels = c("V", "S"))
   am <- factor(am, labels = c("automatic", "manual"))
   cyl  <- ordered(cyl)
   gear <- ordered(gear)
   carb <- ordered(carb)
})
summary(my_mtcars2)
```

## First analysis, fuel consumtion.

I want to assess the motors consumption as a function of the displacement.
Engine displacement is the measure of the cylinder volume swept by all of the pistons of a piston engine, excluding the combustion chambers.

```{r mpg_disp, include=TRUE, fig.align='center', fig.width=5, fig.height=5}
plot(mpg ~ disp, data = my_mtcars,xlab="Displacement (cu.in.)",ylab="Fuel consumption Miles/gallon", ylim=c(10,40))
arrows(x0 = my_mtcars$disp, y0 = my_mtcars$mpg * 0.95, x1 = my_mtcars$disp, y1 = my_mtcars$mpg * 
    1.05, angle = 90, code = 3, length = 0.04, lwd = 0.4, col="red")
```

Whoo, that was **interesting**. Can we concldude that biggers motors consume more fuel?

Let's move on to the next analysis.

## Second analysis, is that all?
To assess whether other variables could also explain the consumption I will plot the correlation among each pair of variables in my data.
```{r mtcorplot, fig.align='center', fig.width=8, fig.height=8}
mcor <- cor(my_mtcars)
corrplot(mcor)
```
Whoohoohooo, that plot looks great!

It looks like the **number of cylinders** (cyl), **Gross horsepower** (hp) and the **Weight** (wt. 1000 lbs), could play a role too.

If you are looking for the the variables meaning, you can find it [here](https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/mtcars)


## Third analysis, we like camembert, they like pie!
Lets produce a pie chart showing the proportion of cars that have different carb values.

```{r ho_mae, fig.align='right', fig.width=8, fig.height=6, fig.cap="Figure 1: have you ever tried the camenbert pie"}
#concat the names for the legend
names = as.factor(paste(unique(my_mtcars$carb),"carbs"))
#get the percentages
percent=100*table(my_mtcars$carb)/length(my_mtcars$carb)
pie(x=percent, label=paste(percent, "%"),  col=rainbow(length(names)), main="Percentage of cars per number of carburators" ) 
#add legend
legend("right",legend = names, fill = rainbow(length(names)), cex=0.8)
```

# Let's make sure that my figures have been saved!

```{r}
list.dirs(path = ".", full.names = TRUE, recursive = TRUE)
list.files(path = "./Exercise_files/figure-html/")
```

# Print a nice table of....


```{r}
table(my_mtcars2$gear,my_mtcars2$carb)
```



# Bibliography


